Fourier-domain modulations and delays of gravitational-wave signals

### 2018-04-05 docs/paper_method.tex
Small changes and edits to the paper.
- added y12 along y12L in the time-domain response
- default for bambi parameter eff changed from 0.1 to 0.5
- edits to the paper

First, we should mention that these signals share similarities with the galactic binaries that will provide numerous quasi-monochromatic signals in the LISA band~\cite{LISA17}. They are far from merger, slowly chirping, and span only a narrow frequency band over the course of the LISA mission lifetime. For the galactic binaries, an accurate and very efficient numerical treatment of the response has been proposed in~\cite{} \SM{[C]} and widely used in applications (see e.g.~\cite{} \SM{[C]}). This treatment is referred to as the fast-slow decomposition, or heterodyning approach. If the gravitational wave signal extends only on the narrow frequency band $f \in [f_{*}, (1+\eta) f_{*}]$ with $\eta \ll 1$, then scaling out a carrier frequency of the signal by multpilying by $e^{-2 i \pi f_{*} t}$ will eliminate most of the time variability, allowing to process the signal through the time-domain response and to take a FFT with a Nyquist frequency shifted from $(1+\eta) f_{*}$ to $\eta f_{*}$, i.e. with a much smaller number of samples. This multiplication is simply equivalent to a shift in frequency domain, which can be restored after the numerical FFT has been computed. The efficiency of this approach is contingent to the smallness of $\eta$. For galactic binaries, this quantity is typically \SM{[complete]}. For SOBH systems, however, $\eta$ will take a continuous set of values from roughly $10^{-4}$ to $1$ \SM{[check values]}. Although the systems for which $\eta$ is the largest are also the easiest to treat with the perturbative formalism of Sec~\ref{sec:formalism}, we propose here yet a third method for dealing with potentially troublesome systems. We leave for the future a more detailed study of SOBH systems as a population, and the investigation of the precise boundaries and overlap areas of the three methods as well as their respective computational costs.

@@

Inserting~\eqref{eq:Gdiscretefourier} into the convolution~\eqref{eq:FDkernel} leads to the following generalized discrete convolution:
\be\label{eq:transferdiscreteconvolution}
	\tilde{s}(f) = \sum_{n \in \mathbb{Z}} c_{n}(f - n f_{0}) \tilde{h} (f - n f_{0}) \,.
\ee
Thus, computing the Fourier-domain response now requires to convolve the signal with a discrete comb with frequency-dependent coefficients $c_{n}$. In practice, this sum is to be truncated at $|n|\leq N$, for some finite order $N$ determining the accuracy of the approximation. To assess the expected truncation error, we use a simple criterion based on the $L^{1}$-norm of the $\{c_{n}\}$ sequence. For a given target truncation error $\eta$, we define the truncation $N(f, \eta)$ as the smallest integer such that 
\be\label{eq:criteriontruncationcomb}
	\sum_{|n| > N(f, \eta)} |c_{n}(f)| < \eta \,.
\ee
The truncation order $N(f,\eta)$ is frequency-dependent, and also depends on the orientation angles. For $c_{n}^{L}$, it also determines the number of function evaluations and the cost of the DFT. For $c_{n}^{0}$, the expression~\eqref{eq:cn0} can provide an asymptotic bound on the width of the comb. For large values of $n$ we have indeed the equivalent $| J_{n}[z] | \sim (e z/2n)^{n}/\sqrt{2\pi n} \; \left[ n\rightarrow + \infty \right]$~\cite{} \SM{[C: dlmf?]}, so that a conservative estimate for the truncation order (almost independent of $\eta$) is given by $N \geq  |e \pi f R \cos \beta|$. Fig.~\ref{fig:lisacombextent} shows numerical computations for $N(f,\eta)$, averaged over orientation angles, for both the constellation and the orbital response and for the truncation levels  $\eta=10^{-12}$, $10^{-6}$, $10^{-3}$. We see that, especially at high frequencies, the orbital response requires more coefficients than the constellation response due to the longer baseline of the delay. At the frequency $f=0.1\Hz$, we have for the orbital response $N \simeq 200$.

@@

We define $(\alpha, \beta, \gamma)$ are the Euler angles relating the precessing frame to the inertial frame in the $(z,y,z)$ convention. The $z$ axis of the inertial frame is chosen to be the direction of $\bm{J}$, the total angular momentum, which is almost constant\footnote{Except in the cases of transitional precession~\cite{Apostolatos+94}, where for high mass ratios and large antialigned spins the orbital angular momentum and the spin can almost cancel each other.}. The first two angles, $\alpha$ and $\beta$, are the two spherical angles tracking the direction of dominant radiation reaction, which during the inspiral follows essentially the normal to the orbital plane. The last angle $\gamma$ parametrizes the remaining freedom of rotation around this radiation axis. An important element of the construction of the precessing frame is the fixing of this third degree of freedom, for which we use the minimal rotation condition~\cite{Boyle+11}
\be\label{eq:gammadot}
	\dot{\gamma} = -\dot{\alpha}\cos \beta \,.
\ee
Quite generically, and in particular in the case of simple precession~\cite{Apostolatos+94, Kidder95} but also in the model we will take for the post-merger precession, the radiation axis precesses on a cone around the direction of $\bm{J}$, with $\alpha$ increasing, while $\beta$, the opening angle of the precession cone, is slowly varying.

@@

For the extension of the frame trajectory post-merger, we do not rely on the PhenomP procedure as it is merely effective. Furthermore, we found that the ringdown attachment procedure, as implemented in SEOB, leads to frame trajectories that show oscillations in all the Euler angles when the spins are anti-aligned. These oscillations increase in amplitude as the spins go to larger misalignments, and are already present well beneath the regime of transitional precession. Since we checked that the qualitative behaviour~\eqref{eq:OmegaframeQNM} holds rather well for numerical relativity simulations in regions of the parameter space where SEOB starts to show these oscillations, and since the SEOB post-merger ringdown attachment is an effective representation, we chose to use an artificial post-merger extension of the frame, following
\be\label{eq:alphaQNM}
	\alpha_{\rm post-merger}(t) = \alpha(t_{\rm peak}) + (\omega_{220}^{\rm QNM} - \omega_{210}^{\rm QNM})(t-t_{\rm peak}) \,.
\ee
Since we do not have yet a quantitative model of the behaviour of the opening angle of the precessing cone $\beta$, we simply set it to a constant value post-merger, taken to be its value at merger. The third Euler angle $\gamma$ is extended using the minimal rotation condition~\eqref{} \SM{[R]}. For the QNM frequencies as a function of the final spin, we use values tabulated in Ref.~\cite{} \SM{[C]}. The final spin is taken to be the same as in the SEOB code~\cite{} \SM{[C]}, where the final-spin fit formula of Ref.~\cite{} \SM{[C]}, built for spin-aligned systems, is applied to the spin components \SM{[check that and complete]}. Our simple extension is an idealization, especially for the angle $\beta$, and is not to be considered quantitatively accurate. However, it allows us to capture what we believe to be the dominant post-merger behaviour, in the sense that the frame is set to rotate with a velocity of the right order of magnitude, which is crucial for us since we want to investigate how the separation between the orbital (or $h^{\rm P}_{\ell m}$) timescale and the precessing timescale is challenged post-merger. We show in Fig~\ref{} the frequencies $\omega_{220}^{\rm QNM}$, $\omega_{210}^{\rm QNM}$ and their difference $\Omega_{\rm frame}$. The behaviour for near-to-extremal spin of the remnant would require more exploration, as the QNM frequencies vary a lot when approaching extramality. \SM{[add plot of QNM frequency and frequency diff according to final spin]}.  Fig.~\ref{fig:prectoymodel} presents a comparison of the frame trajectory at merger for the SEOB, NR waveforms and for our model. The example catalog waveform is SXS:BBH:0058~\cite{} \SM{[C]}, which presents a rather high mass ratio of $q=5$, with a single spin in-plane of $\chi_{1} = 0.5$. The NR and SEOB post-merger frames disagree mainly due to a different value of the final spin $\chi_{f}$\footnote{Work is underway to update the fit formulas used to compute $\chi_{f}$ in the SEOB code, which is expected to reduce these disagreement~\cite{}. \SM{[C]} \SM{[work in preparation by SEOB people, essentially already done]}}, which leads to a different $\Omega_{\rm frame}$. Given their different value of $\chi_{f}$, however, both agree with the qualitative prescription~\eqref{eq:OmegaframeQNM}. The oscillations developing after $t\sim 50 M$ occur in a regime where the overall waveform amplitude has decayed to small values, and are not important in that regard. Our model follows well the SEOB behaviour for $\alpha$ and $\gamma$, but departs more for $\beta$ as it ignores its variation at merger.

@@

@@

For the inspiral phase of the dynamics, one can read the quantities $\epsilon_{\Psi 2}$, $\epsilon_{A1}$ and $\epsilon_{A 2}$ from the outcome of post-Newtonian computations. To obtain a qualitative picture of the timescales involved, here we will consider the most simple setting for precession in the post-Newtonian framework: at leading PN order and for a single-spin system, both the orbital angular momentum $\bm{L}$ and the spin vector $\bm{S}$ undergo what is called simple precession around the total angular momentum, $\bm{J}$ (see e.g.~\cite{Apostolatos+94, Kidder95}). By neglecting the slow evolution of the orbit under radiation reaction, ignoring higher-order corrections that are quadratic and higher in the spins, and orbit-averaging the precession equations (thus eliminating nutations in the precession of the orbital plane, which occur at the orbital timescale), the trajectories of $\bm{L}$ and $\bm{S}$ become cones around the direction of $\bm{J}$, with a constant precession velocity $\Omega_{\rm prec}$ that we will use to define the timescale of variations of the modulation functions $F$. Note that the presence of two spins complicates the evolution of the system, but the picture of a precession cone for $\bm{\ell}$ remains approximately valid (see~\cite{} \SM{[C]} for a classification of the morphologies of precessing trajectories).

@@

In our convention, the link between the Discrete Fourier Transform (DFT) \SM{[check acronym]} and the trigonometric polynomial representation of a function goes as follows. For a periodic function $F(x)$ defined on $x\in [x_{0}, x_{0} + \Delta x]$, and represented by $N$ samples $x_{j} = \ov{x} + j \Delta x/N$, $j=0,\dots,N-1$, with $N$ large enough to satisfy, at least approximately, the Nyquist criterion, we can build a trigonometric interpolant $P(x)$ as
\be
	P(x) = \sum\limits_{k=-M}^{+M} c_{k} e^{2i\pi k \frac{x-x_{0}}{\Delta x}} \,,
\ee
that will satisfy the system $P(x_{j}) = F(x_{j})$ for $j=0,\dots, N-1$. Here we set $M=N/2$, assuming N is even. This trigonometric polynomial representation is equivalent to truncating the formal Fourier series, representing the full signal, to a finite order $M$. The coefficients $c_{k}$, in the full series, are defined as integrals over the interval of $F$ weighted by the appropriate exponential (as in~\eqref{eq:defcn}). In both interpretations, either the truncated approximation of the Fourier series or  the trigonometric interpolation formulation, these coefficients are related to the coefficients of the inverse DFT. If we set $\omega \equiv e^{2i\pi/N}$ and define
\be\label{eq:ykDFT}
	y_{k} = \frac{1}{N} \sum\limits_{j=0}^{N-1} F(x_{j}) \omega^{jk} \,,
\ee
which is the expression of the inverse DFT in our sign convention~\eqref{eq:defFT}, the coefficients $c_{k}$ are given by
\begin{align}\label{eq:ckyk}
	c_{k} &= y_{k} \text{ for } k=0,\dots, M-1 \,, \nn\\
	c_{k} &= y_{k+N} \text{ for } k=-M+1,\dots, -1 \,, \nn\\
	c_{M} &= c_{-M} = \frac{y_{M}}{2} \,,
\end{align}
where the condition $c_{M} = c_{-M}$ is an arbitrary condition enforced to match the number of degrees of freedom. In practice, a good representation of the Fourier series of the signal is achieved when the truncation order $M$ is sufficient so that the coefficients $c_{|n|\geq M}$ become negligibly small.

@@

In this Appendix, we give explicit expressions for the stencil coefficients entering~\eqref{eq:stencilfresnel}. In this work we used only low order stencils with usually $N\leq 5$, and one can simply numerically invert of the system~\eqref{eq:stencilsystem}, as this operation has to be done only once. For future reference, we give here exact expressions, as the specific choice of samples at $\pm kT$ gives to the system~\eqref{eq:stencilsystem} the form of a Vandermonde system. Defining the Vandermonde matrix $V(x_{0},\dots,x_{N})$ as $V_{ij} = (x_{j})^{i}$, setting $x_{j} = j^{2}$, and $b_{p} \equiv (-i\epsilon)^{p}(2p-1)!!$, the linear system~\eqref{eq:stencilsystem} becomes
\be
	b_{p} = \sum\limits_{k=0}^{N} V_{p,k} a_{N,k}^{\epsilon} \,.
\ee
%Now, since the Vandermonde system can be seen as a reformulation of the polynomial interpolation problem, we know that $({}^{t}V^{-1})_{ij}$ is the coefficient of $X^{i}$ in the Lagrange interpolation polynomial $\prod_{k\neq j} (X-x_{k})/(x_{j} - x_{k})$. If we introduce the symmetric polynomials $\sigma$ such that
%\be	
%	\sigma(m, \{x_{1}, \dots, x_{n}\}) = \sum\limits_{1\leq i_{1}<\dots<i_{m}\leq n} x_{i_{1}}\dots x_{i_{m}} \,,
%\ee
%we obtain for the inverse of the matrix $V$
%\be
%	V^{-1}_{ij} = \frac{1}{\prod_{k\neq i} (i^{2} - k^{2})} (-1)^{N-j} \sigma(N-j, \{0,\dots,N^{2}\}\backslash \{i^{2}\}) \,.
%\ee
The expression of the inverse of a Vandermonde matrix in terms of symmetric polynomials then allows us to write a closed-form (but rather impractical) expression for the $a_{N,k}^{\epsilon}$, for every finite order $N$:
\begin{align}
	a_{N,k}^{\epsilon} &= \frac{1}{\prod\limits_{\substack{q=0 \\ q\neq k}}^{N} (q^{2}-k^{2})} \sum\limits_{p=0}^{N} (i\epsilon)^{p}(2p-1)!! \nn\\ & \quad \cdot \sum\limits_{\substack{ 0 \leq j_{1} < \dots < j_{N-p} \leq N \\ j_{1}, \dots, j_{N-p} \neq k}} j_{1}^{2}\dots j_{N-p}^{2}
\end{align}
The two cases $\epsilon\pm 1$ correspond simply to a complex conjugation of the coefficients $a_{N,k}^{\epsilon}$. Table~\ref{table:stencil} gives the resulting rational values for these coefficients for $N\leq 5$.

>>>>

First, we should mention that these signals share similarities with the galactic binaries that will provide numerous quasi-monochromatic signals in the LISA band~\cite{LISA17}. They are far from merger, slowly chirping, and span only a narrow frequency band over the course of the LISA mission lifetime. For the galactic binaries, an accurate and very efficient numerical treatment of the response has been proposed in~\cite{} \SM{[C]} and widely used in applications (see e.g.~\cite{} \SM{[C]}). This treatment is referred to as the fast-slow decomposition, or heterodyning approach. If the gravitational wave signal extends only on the narrow frequency band $f \in [f_{*}, (1+\eta) f_{*}]$ with $\eta \ll 1$, then scaling out a carrier frequency of the signal by multpilying by $e^{-2 i \pi f_{*} t}$ will eliminate most of the time variability, allowing to process the signal through the time-domain response and to take a FFT with a Nyquist frequency shifted from $(1+\eta) f_{*}$ to $\eta f_{*}$, i.e. with a much smaller number of samples. This multiplication is simply equivalent to a shift in frequency domain, which can be restored after the numerical FFT has been computed. The efficiency of this approach is contingent to the smallness of $\eta$. For galactic binaries, this quantity is typically \SM{[complete]}. For SOBH systems, however, $\eta$ will take a continuous set of values from roughly $10^{-4}$ to $1$ \SM{[check values]}. \SM{[add sentence: cover the intermediate ground]} Although the systems for which $\eta$ is the largest are also the easiest to treat with the perturbative formalism of Sec~\ref{sec:formalism}, we propose here yet a third method for dealing with potentially troublesome systems. We leave for the future a more detailed study of SOBH systems as a population, and the investigation of the precise boundaries and overlap areas of the three methods as well as their respective computational costs.

@@

Inserting~\eqref{eq:Gdiscretefourier} into the convolution~\eqref{eq:FDkernel} leads to the following generalized discrete convolution:
\be\label{eq:transferdiscreteconvolution}
	\tilde{s}(f) = \sum_{n \in \mathbb{Z}} c_{n}(f - n f_{0}) \tilde{h} (f - n f_{0}) \,.
\ee
Thus, computing the Fourier-domain response now requires to convolve the signal with a discrete comb with frequency-dependent coefficients $c_{n}$. In practice, this sum is to be truncated at $|n|\leq N$, for some finite order $N$ determining the accuracy of the approximation. To assess the expected truncation error, we use a simple criterion based on the $L^{1}$-norm of the $\{c_{n}\}$ sequence. For a given target truncation error $\eta$, we define the truncation \SM{change notation to avoid confusion with $N$ from Fresnel stencil} $N(f, \eta)$ as the smallest integer such that 
\be\label{eq:criteriontruncationcomb}
	\sum_{|n| > N(f, \eta)} |c_{n}(f)| < \eta \,.
\ee
The truncation order $N(f,\eta)$ is frequency-dependent, and also depends on the orientation angles. For $c_{n}^{L}$, it also determines the number of function evaluations and the cost of the DFT. For $c_{n}^{0}$, the expression~\eqref{eq:cn0} can provide an asymptotic bound on the width of the comb. For large values of $n$ we have indeed the equivalent $| J_{n}[z] | \sim (e z/2n)^{n}/\sqrt{2\pi n} \; \left[ n\rightarrow + \infty \right]$~\cite{} \SM{[C: dlmf?]}, so that a conservative estimate for the truncation order (almost independent of $\eta$) is given by $N \geq  |e \pi f R \cos \beta|$. Fig.~\ref{fig:lisacombextent} shows numerical computations for $N(f,\eta)$, averaged over orientation angles, for both the constellation and the orbital response and for the truncation levels  $\eta=10^{-12}$, $10^{-6}$, $10^{-3}$. We see that, especially at high frequencies, the orbital response requires more coefficients than the constellation response due to the longer baseline of the delay. At the frequency $f=0.1\Hz$, we have for the orbital response $N \simeq 200$.

@@

We define $(\alpha, \beta, \gamma)$ are the Euler angles relating the precessing frame to the inertial frame in the $(z,y,z)$ convention. The $z$ axis of the inertial frame is chosen to be the direction of $\bm{J}$, the total angular momentum, which is almost constant\footnote{Except in the cases of transitional precession~\cite{Apostolatos+94}, where for high mass ratios and large antialigned spins the orbital angular momentum and the spin can almost cancel each other.}. The first two angles, $\alpha$ and $\beta$, are the two spherical angles tracking the direction of dominant radiation reaction, which during the inspiral follows essentially the normal to the orbital plane. The last angle $\gamma$ parametrizes the remaining freedom of rotation around this radiation axis. An important element of the construction of the precessing frame is the fixing of this third degree of freedom, for which we use the minimal rotation condition~\cite{Boyle+11} \SM{[explain what it means]}
\be\label{eq:gammadot}
	\dot{\gamma} = -\dot{\alpha}\cos \beta \,.
\ee
Quite generically, and in particular in the case of simple precession~\cite{Apostolatos+94, Kidder95} but also in the model we will take for the post-merger precession, the radiation axis precesses on a cone around the direction of $\bm{J}$, with $\alpha$ increasing, while $\beta$, the opening angle of the precession cone, is slowly varying.

@@

For the extension of the frame trajectory post-merger, we do not rely on the PhenomP procedure as it is merely effective \SM{[be clearer on the limitation here]}. Furthermore, we found that the ringdown attachment procedure, as implemented in SEOB, leads to frame trajectories that show oscillations in all the Euler angles when the spins are anti-aligned. These oscillations increase in amplitude as the spins go to larger misalignments, and are already present well beneath the regime of transitional precession. Since we checked that the qualitative behaviour~\eqref{eq:OmegaframeQNM} holds rather well for numerical relativity simulations in regions of the parameter space where SEOB starts to show these oscillations, and since the SEOB post-merger ringdown attachment is an effective representation, we chose to use an artificial post-merger extension of the frame, following
\be\label{eq:alphaQNM}
	\alpha_{\rm post-merger}(t) = \alpha(t_{\rm peak}) + (\omega_{220}^{\rm QNM} - \omega_{210}^{\rm QNM})(t-t_{\rm peak}) \,.
\ee
Since we do not have yet a quantitative model of the behaviour of the opening angle of the precessing cone $\beta$, we simply set it to a constant value post-merger, taken to be its value at merger. The third Euler angle $\gamma$ is extended using the minimal rotation condition~\eqref{} \SM{[R]}. For the QNM frequencies as a function of the final spin, we use values tabulated in Ref.~\cite{} \SM{[C]}. The final spin is taken to be the same as in the SEOB code~\cite{} \SM{[C]}, where the final-spin fit formula of Ref.~\cite{} \SM{[C]}, built for spin-aligned systems, is applied to the spin components \SM{[check that and complete]}. Our simple extension is an idealization, especially for the angle $\beta$, and is not to be considered quantitatively accurate. However, it allows us to capture what we believe to be the dominant post-merger behaviour, in the sense that the frame is set to rotate with a velocity of the right order of magnitude, which is crucial for us since we want to investigate how the separation between the orbital (or $h^{\rm P}_{\ell m}$) timescale and the precessing timescale is challenged post-merger. We show in Fig~\ref{} the frequencies $\omega_{220}^{\rm QNM}$, $\omega_{210}^{\rm QNM}$ and their difference $\Omega_{\rm frame}$. The behaviour for near-to-extremal spin of the remnant would require more exploration, as the QNM frequencies vary a lot when approaching extramality. \SM{[add plot of QNM frequency and frequency diff according to final spin]}.  Fig.~\ref{fig:prectoymodel} presents a comparison of the frame trajectory at merger for the SEOB, NR waveforms and for our model. The example catalog waveform is SXS:BBH:0058~\cite{} \SM{[C]}, which presents a rather high mass ratio of $q=5$, with a single spin in-plane of $\chi_{1} = 0.5$. The NR and SEOB post-merger frames disagree mainly due to a different value of the final spin $\chi_{f}$\footnote{Work is underway to update the fit formulas used to compute $\chi_{f}$ in the SEOB code, which is expected to reduce these disagreement~\cite{}. \SM{[C]} \SM{[work in preparation by SEOB people, essentially already done]}}, which leads to a different $\Omega_{\rm frame}$. Given their different value of $\chi_{f}$, however, both agree with the qualitative prescription~\eqref{eq:OmegaframeQNM}. The oscillations developing after $t\sim 50 M$ occur in a regime where the overall waveform amplitude has decayed to small values, and are not important in that regard. Our model follows well the SEOB behaviour for $\alpha$ and $\gamma$, but departs more for $\beta$ as it ignores its variation at merger.

@@

\SM{[write somewhere that we require mainly FD smoothness]}

@@

For the inspiral phase of the dynamics, one can read the quantities $\epsilon_{\Psi 2}$, $\epsilon_{A1}$ and $\epsilon_{A 2}$ from the outcome of post-Newtonian computations. To obtain a qualitative picture of the timescales involved, here we will consider the most simple setting for precession in the post-Newtonian framework: at leading PN order and for a single-spin system, both the orbital angular momentum $\bm{L}$ and the spin vector $\bm{S}$ undergo what is called simple precession around the total angular momentum, $\bm{J}$ (see e.g.~\cite{Apostolatos+94, Kidder95}). By neglecting the slow evolution of the orbit under radiation reaction, ignoring higher-order corrections that are quadratic and higher in the spins, and orbit-averaging the precession equations (thus eliminating nutations in the precession of the orbital plane, which occur at the orbital timescale) \SM{[no nutation for single spin?]}, the trajectories of $\bm{L}$ and $\bm{S}$ become cones around the direction of $\bm{J}$, with a constant precession velocity $\Omega_{\rm prec}$ that we will use to define the timescale of variations of the modulation functions $F$. Note that the presence of two spins complicates the evolution of the system, but the picture of a precession cone for $\bm{\ell}$ remains approximately valid (see~\cite{} \SM{[C]} for a classification of the morphologies of precessing trajectories).

@@

In our convention, the link between the Discrete Fourier Transform (DFT) \SM{[check acronym]} and the trigonometric polynomial representation of a function goes as follows. For a periodic function $F(x)$ defined on $x\in [x_{0}, x_{0} + \Delta x]$, and represented by $N$ samples $x_{j} = \ov{x} + j \Delta x/N$, $j=0,\dots,N-1$, with $N$ large enough to satisfy, at least approximately, the Nyquist criterion, we can build a trigonometric interpolant $P(x)$ as
\be
	P(x) = \sum\limits_{k=-M}^{+M} c_{k} e^{2i\pi k \frac{x-x_{0}}{\Delta x}} \,,
\ee
that will satisfy the system $P(x_{j}) = F(x_{j})$ for $j=0,\dots, N-1$. Here we set $M=N/2$, assuming N is even. This trigonometric polynomial representation is equivalent to truncating the formal Fourier series, representing the full signal, to a finite order $M$. The coefficients $c_{k}$, in the full series, are defined as integrals over the interval of $F$ weighted by the appropriate exponential (as in~\eqref{eq:defcn}). In both interpretations, either the truncated approximation of the Fourier series or  the trigonometric interpolation formulation, these coefficients are related to the coefficients of the inverse DFT. If we set $\omega \equiv e^{2i\pi/N}$ and define \SM{[check convention]}
\be\label{eq:ykDFT}
	y_{k} = \frac{1}{N} \sum\limits_{j=0}^{N-1} F(x_{j}) \omega^{jk} \,,
\ee
which is the expression of the inverse DFT in our sign convention~\eqref{eq:defFT}, the coefficients $c_{k}$ are given by
\begin{align}\label{eq:ckyk}
	c_{k} &= y_{k} \text{ for } k=0,\dots, M-1 \,, \nn\\
	c_{k} &= y_{k+N} \text{ for } k=-M+1,\dots, -1 \,, \nn\\
	c_{M} &= c_{-M} = \frac{y_{M}}{2} \,,
\end{align}
where the condition $c_{M} = c_{-M}$ is an arbitrary condition enforced to match the number of degrees of freedom. In practice, a good representation of the Fourier series of the signal is achieved when the truncation order $M$ is sufficient so that the coefficients $c_{|n|\geq M}$ become negligibly small.

@@

In this Appendix, we give explicit expressions for the stencil coefficients entering~\eqref{eq:stencilfresnel}. In this work we used only low order stencils with usually $N\leq 5$, and one can simply numerically invert of the system~\eqref{eq:stencilsystem}, as this operation has to be done only once. For future reference, we give here exact expressions, as the specific choice of samples at $\pm kT$ gives to the system~\eqref{eq:stencilsystem} the form of a Vandermonde system. Defining the Vandermonde matrix $V(x_{0},\dots,x_{N})$ as $V_{ij} = (x_{j})^{i}$, setting $x_{j} = j^{2}$, and $b_{p} \equiv (-i\epsilon)^{p}(2p-1)!!$, the linear system~\eqref{eq:stencilsystem} becomes
\be
	b_{p} = \sum\limits_{k=0}^{N} V_{p,k} a_{N,k}^{\epsilon} \,.
\ee
%Now, since the Vandermonde system can be seen as a reformulation of the polynomial interpolation problem, we know that $({}^{t}V^{-1})_{ij}$ is the coefficient of $X^{i}$ in the Lagrange interpolation polynomial $\prod_{k\neq j} (X-x_{k})/(x_{j} - x_{k})$. If we introduce the symmetric polynomials $\sigma$ such that
%\be	
%	\sigma(m, \{x_{1}, \dots, x_{n}\}) = \sum\limits_{1\leq i_{1}<\dots<i_{m}\leq n} x_{i_{1}}\dots x_{i_{m}} \,,
%\ee
%we obtain for the inverse of the matrix $V$
%\be
%	V^{-1}_{ij} = \frac{1}{\prod_{k\neq i} (i^{2} - k^{2})} (-1)^{N-j} \sigma(N-j, \{0,\dots,N^{2}\}\backslash \{i^{2}\}) \,.
%\ee
The expression of the inverse of a Vandermonde matrix in terms of symmetric polynomials then allows us to write a closed-form (but rather impractical) expression for the $a_{N,k}^{\epsilon}$, for every finite order $N$:
\begin{align}
	a_{N,k}^{\epsilon} &= \frac{1}{\prod\limits_{\substack{q=0 \\ q\neq k}}^{N} (q^{2}-k^{2})} \sum\limits_{p=0}^{N} (i\epsilon)^{p}(2p-1)!! \nn\\ & \quad \cdot \sum\limits_{\substack{ 0 \leq j_{1} < \dots < j_{N-p} \leq N \\ j_{1}, \dots, j_{N-p} \neq k}} j_{1}^{2}\dots j_{N-p}^{2}
\end{align}
The two cases $\epsilon\pm 1$ correspond simply to a complex conjugation of the coefficients $a_{N,k}^{\epsilon}$. Table~\ref{table:stencil} gives the resulting complex rational values for these coefficients for $N\leq 5$.
